### 2024-12-01 paper/paper.qmd
update data section
update graphs in paper.qmd

# Graph histogram
# Calculate the mean of diamond prices
mean_price <- mean(cleaned_data$price, na.rm = TRUE)
# Create the histogram with mean line and density curve
histogram_plot <- ggplot(cleaned_data, aes(x = price)) +
  geom_histogram(binwidth = 500, fill = "pink", color = "black", alpha = 0.7) + 
  geom_vline(xintercept = mean_price, linetype = "dashed", color = "salmon") + # Add a dashed vertical line for the mean
  labs(
    x = "Diamond Price",
    y = "Count"
  ) +
  theme_minimal() # Use a minimal theme for clean visualization

# Graph boxplot
boxplot <- ggplot(cleaned_data, aes(x = "", y = price)) +
  geom_boxplot(fill = "lightblue", color = "black", alpha = 0.7, outlier.colour = "salmon") +
  labs(
    x = "",
    y = "Diamond Price"
  ) +
  theme_minimal()

@@

color_histogram_plot <- ggplot(cleaned_data, aes(x = color)) +
  geom_bar(binwidth = 3,fill = "lightblue", color = "black", alpha = 0.7) + 
  #scale_x_continuous(
  #  breaks = 1:8, 
  #  labels = c("D", "E", "F", "G", "H", "I", "J", "K"))+
  labs(
    title ="Distribution of Variable: Color",
    x = "Diamond Color",
    y = "Count") +
  theme_minimal() # Use a minimal theme for clean visualization

plot_color <- ggplot(cleaned_data, aes(x = color, y = price,group = 1))+
  geom_point(color = "pink", alpha = 0.7) + 
  geom_smooth(method = "lm", color = "black", se = FALSE) + 
  labs(
    title = "Color vs Price",
    x = "Color",
    y = "Diamond Price"
  ) +
  theme_minimal()

combined_plot <- color_histogram_plot | plot_color
combined_plot

@@

# Graph histogram
# Create the histogram with mean line
clarity_histogram_plot <- ggplot(cleaned_data, aes(x = clarity)) +
  geom_bar(bins = 20, fill = "lightblue", color = "black", alpha = 0.7) +
  labs(
    title = "Distribution of Variable: Clarity",
    x = "Diamond Clarity",
    y = "Count"
  ) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plot_clarity <- ggplot(cleaned_data, aes(x = clarity, y = price, group=1)) +
  geom_point(color = "pink", alpha = 0.7) +
  geom_smooth(method = "loess", color = "black", se = FALSE) +
  labs(
    title = "Clarity vs Price",
    x = "Clarity",
    y = "Diamond Price"
  ) +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Combine 2 plots
combined_plot <- clarity_histogram_plot | plot_clarity
combined_plot

@@

# Graph histogram
# Create the histogram with mean line
clarity_histogram_plot <- ggplot(cleaned_data, aes(x = cut)) +
  geom_bar(bins = 20, fill = "palevioletred", color = "black", alpha = 0.7)+
  labs(
    title = "Distribution of Variable: Cut",
    x = "Diamond Cut",
    y = "Count"
  ) +
  theme_minimal() # Use a minimal theme for clean visualization

plot_cut <- ggplot(cleaned_data, aes(x = cut, y = price,group=1)) +
  geom_point(color = "lightblue", alpha = 0.7) +
  geom_smooth(method = "loess", color = "black", se = FALSE) +
  labs(
    title = "Cut vs Price",
    x = "Cut",
    y = "Diamond Price"
  ) +
  theme_minimal()

# Combine 2 plots
combined_plot <- clarity_histogram_plot | plot_cut
combined_plot

@@

>>>>

# Graph histogram
# Calculate the mean of diamond prices
mean_price <- mean(cleaned_data$price, na.rm = TRUE)
# Create the histogram with mean line and density curve
histogram_plot <- ggplot(cleaned_data, aes(x = price)) +
  geom_histogram(binwidth = 500, fill = "lightblue", color = "black", alpha = 0.7) + 
  geom_vline(xintercept = mean_price, linetype = "dashed", color = "salmon") + # Add a dashed vertical line for the mean
  labs(
    x = "Diamond Price",
    y = "Count"
  ) +
  theme_minimal() # Use a minimal theme for clean visualization

# Graph boxplot
boxplot <- ggplot(cleaned_data, aes(x = "", y = price)) +
  geom_boxplot(fill = "pink", color = "black", alpha = 0.7, outlier.colour = "salmon") +
  labs(
    x = "",
    y = "Diamond Price"
  ) +
  theme_minimal()

@@

color_histogram_plot <- ggplot(cleaned_data, aes(x = color)) +
  geom_bar(binwidth = 3,fill = "pink", color = "black", alpha = 0.7) + 
  #scale_x_continuous(
  #  breaks = 1:8, 
  #  labels = c("D", "E", "F", "G", "H", "I", "J", "K"))+
  labs(
    title ="Distribution of Variable: Color",
    x = "Diamond Color",
    y = "Count") +
  theme_minimal() # Use a minimal theme for clean visualization

# 绘制小提琴图
violin_plot_color <- ggplot(cleaned_data, aes(x = color, y = price)) +
  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) +  # 添加小提琴图
  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +  # 在小提琴图中叠加箱线图
  labs(
    title = "Violin Plot of Price by Color",
    x = "Color",
    y = "Price"
  ) +
  theme_minimal()  # 使用简洁的主题

# Combine 2 plots
combined_plot <- color_histogram_plot | violin_plot_color
combined_plot
```

@@

# Graph histogram
# Create the histogram with mean line
clarity_histogram_plot <- ggplot(cleaned_data, aes(x = clarity)) +
  geom_bar(bins = 20, fill = "pink", color = "black", alpha = 0.7) +
  labs(
    title = "Distribution of Variable: Clarity",
    x = "Diamond Clarity",
    y = "Count"
  ) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

boxplot_plot_clarity <- ggplot(cleaned_data, aes(x = clarity, y = price)) +
  geom_boxplot(fill = "lightblue",outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +
  labs(
    title = "Boxplot of Price by Clarity",
    x = "Cut",
    y = "Price"
  ) +
  theme_minimal()

# Combine 2 plots
combined_plot <- clarity_histogram_plot | boxplot_plot_clarity
combined_plot

@@

# Graph histogram
# Create the histogram with mean line
cut_histogram_plot <- ggplot(cleaned_data, aes(x = cut)) +
  geom_bar(bins = 20, fill = "palevioletred", color = "black", alpha = 0.7)+
  labs(
    title = "Distribution of Variable: Cut",
    x = "Diamond Cut",
    y = "Count"
  ) +
  theme_minimal() # Use a minimal theme for clean visualization

violin_plot_cut <- ggplot(cleaned_data, aes(x = cut, y = price)) +
  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) + 
  geom_boxplot(width = 0.2, outlier.cut = "salmon", outlier.shape = 8, alpha = 0.7) +
  labs(
    title = "Violin Plot of Price by Cut",
    x = "Cut",
    y = "Price"
  ) +
  theme_minimal()

# Combine 2 plots
combined_plot <- cut_histogram_plot | violin_plot_cut
combined_plot

@@

```
Variable type
